Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-10-29 pdocs/thesis/epj-jcgt.tex
work on jcgt article

\paragraph{Limitations}
Forces are calculated by dividing impulse by timestep and maximum impulse is calculated
by multiplying maximum force by timestep. 
This means that simulation of quick interactions requires small timestep.
This limitation is not introduced by this approach but is build in feature of impulse-based simulation.
Bending moment - normal force interactions and multiaxial stress are not taken into account. 
Simulation of many bodies connected by constraints

@@

\begin{figure}[htb]
  \centering
   \includegraphics[height=5cm]{figs/tippingCar1.png}
   \includegraphics[height=5cm]{figs/tippingCar2.png}
   \includegraphics[height=5cm]{figs/tippingCar3.png}
   \caption{\label{fig:tippingCar}
     Large impulse turns car over.}
\end{figure}
Making simulation step smaller is not desired solution.
In this paper following procedure is suggested.

\begin{enumerate}
\item 
\end{enumerate}

\section{Implementation for Box2D}
b2ElasticPlasticJoint implementation is based on b2WeldJoint which implements rigid and flexible joints as
described in Catto's paper~\shortcite{ecsc} on soft constraints. Main idea is that game designer should not have
find suitable values to get desired functionality but constraint is configured by giving desired  damping ratio and frequency.
This principle leads in many cases to quite soft constraints to keep simulation stable. 
b2WeldJoint supports also rigid joint in which case iterative solver creates some flexibility.
If maximum forces and moment are set to very high value b2ElasticPlasticJoint behaves like b2WeldJoint but is slighly slower.

@@

\subsection{Car} 
Dynamic bodies are car (680 kg), wheels (50 kg for each axel), and ramp (2160 kg). 
Ramp is joined to fixed part with b2ElasticPlasticJoint having frequency of 1 Hz.
Maximum elastic rotation is set to 0.12 and maximum plastic rotation to 0.4.
With this configuration own weight or ramp uses about 13 \% of plastic capacity.
After first jump about 50 \% of  plastic capacity is used. Each additional jump uses about 
7 \% of plastic capacity.

>>>>

\paragraph{Limitations}
Forces are calculated by dividing impulse by timestep and maximum impulse is calculated
by multiplying maximum force by timestep. 
This means that simulation of quick interactions requires small timestep.
This limitation is not introduced by this approach but is build in feature of impulse-based simulation.
We discuss few methods to maximize realisticy of simulation of collisions but this issue will need further work.
Bending moment - normal force interactions and multiaxial stress are not taken into account. 
Simulation of many bodies connected by constraints has convergence issues which will also need further work.

@@

\begin{figure}[htb]
  \centering
   \includegraphics[height=5cm]{figs/tippingCar1.png}
   \includegraphics[height=5cm]{figs/tippingCar2.png}
   \includegraphics[height=5cm]{figs/tippingCar3.png}
   \caption{\label{fig:tippingCar}
     Large impulse turns car over.}
\end{figure}
Making simulation step smaller is not desired solution.
In this paper following procedure suggested.

\begin{enumerate}
\item At start of each step predict outcome of current step for each joint using current velocities and
maximum and current strains and rotations.
\item If current impulse is about to break constraint within current step scale down maximum impulse
so that joint does not exceed planned capacity. 
\end{enumerate}

\paragraph{Impulse initialization}
Joint impulses should be initialized using suitable methods to minimize errors.

\section{Implementation for Box2D}
b2ElasticPlasticJoint implementation is based on b2WeldJoint which implements rigid and flexible joints as
described in Catto's paper~\shortcite{ecsc} on soft constraints. Main idea is that game designer should not have
to find suitable values to get desired functionality but constraint is configured by giving desired  damping ratio and frequency.
This principle leads in many cases to quite soft constraints to keep simulation stable. 
b2WeldJoint supports also rigid joint in which case iterative solver creates some flexibility.
If maximum forces and moment are set to very high value b2ElasticPlasticJoint behaves like b2WeldJoint but is slighly slower.

@@

\subsection{Car} 
Dynamic bodies are car (680 kg), wheels (50 kg for each axel), and ramp (2160 kg). 
Ramp is joined to fixed part with b2ElasticPlasticJoint having frequency of 1 Hz.
Maximum elastic rotation is set to 0.12 and maximum plastic rotation to 0.4.
With this configuration own weight of ramp uses about 13 \% of plastic capacity during initialization phase.
After first jump about 50 \% of  plastic capacity is used. Each additional jump uses about 
7 \% of plastic capacity.
